%=============================================================================%
%Change the font size of your document - 10pt, 12.1pt, etc.
\documentclass[a4paper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{hyperref}

\graphicspath{ {images/}} %upload your signature to this file
%Change the margins to fit your CV/resume content
\usepackage[left=1in, right=1in, bottom=1.25in, top=1.25in]{geometry}


%Changes the page numbers - {arabic}=arabic numerals, {gobble}=no page numbers, {roman}=Roman numerals
\pagenumbering{gobble}
%=============================================================================%
\begin{document}

%-----------------------------------------------------------------------------%

\noindent  \LARGE{\textbf{Matthew J. D. Curtis}}  \\

%\hline 
\normalsize



%-----------------------------------------------------------------------------%

\noindent \begin{longtable}{@{} p{0.175\linewidth} p{0.775\linewidth} p{0.05\linewidth}}
   
   
   
   \textbf{\large{Contact}}    &  \multicolumn{2}{l}{Email: \href{mailto:macu@sam.sdu.dk}{mailto:macu@sam.sdu.dk} }\\
   \textbf{\large{Information}}  &  \multicolumn{2}{l}{Website: \href{https://www.mjdcurtis.com/}{www.mjdcurtis.com} }\\
   %  &  \multicolumn{2}{l}{Phone: +32~491939150}\\
   %     &  \multicolumn{2}{l}{Address: 16 Avenue Dolez, \#1, Uccle 1180, Belgium}\\
   \\ 
   
   \textbf{\large{Employment}}   \\
   &  \multicolumn{2}{l}{  \textbf{Assistant Professor, University of Southern Denmark} \hfill  2023-}\\
   &  \multicolumn{2}{l}{ Postdoctoral researcher, IRES, Universit\'{e} catholic de Louvain \hfill  2023}\\
   &  \multicolumn{2}{l}{ Postdoctoral researcher, ECARES, Universit\'{e} libre de Bruxelles \hfill  2021-2023}\\
   &  \multicolumn{2}{l}{ Senior Research Assistant, Federal Reserve Bank of Boston \hfill  2012-2015}\\
   \\
   \textbf{\large{Education}}    & \multicolumn{2}{l}{\textbf{University of California, Davis}} \\
   &  \multicolumn{2}{l}{Ph.D. in Economics, University of California, Davis, 2021}\\
   &  \multicolumn{2}{l}{BA in Quantitative Economics and Mathematics, Tufts University, 2012}\\
   \\
   
   \textbf{\large{Publications}}   & \textbf{Twins Support Absence of Parity-Dependent Fertility Control in Pretransition Populations }\\
   %& \parbox{5.0in}{ September 2019 – }}\\
   &  with Gregory Clark and Neil Cummins. \href{https://read.dukeupress.edu/demography/article/57/4/1571/168109/Twins-Support-the-Absence-of-Parity-Dependent}{\emph{Demography}}. & \hfill 2020\\
   \\  
   
   \textbf{\large{Working \(\phantom{1}\)  Papers}}  & \textbf{The Her in Inheritance: How Marriage Matching Has Always Mattered, Quebec 1800--1970}\\ 
   &  Job market paper. Revise and resubmit, \emph{Journal of Economic History}. &  \\
   & &
   \\  
   &  \textbf{Was There A Crisis? A Human Development Index for Lower Canada, 1760 to 1848 } \\ 
   &   with Vincent Geloso. Revise and resubmit, \emph{European Review of Economic History}. \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4200516}{SSRN working paper}. &  \\
   \\
   & \textbf{Three New Occupational Status Indices for England and Wales, 1800--1939}\\ 
   &  with Gregory Clark and Neil Cummins. Conditional accept, \emph{Historical Methods}. &   \\
   \\
 
   & \textbf{The Mismeasure of Man: Why Intergenerational Occupational Mobility  is Much Lower than Conventionally Measured, England, 1800--2021}\\ 
   &  with Gregory Clark and Neil Cummins. Submitted. \href{https://hub.cepr.org/published-discussion-paper/139739}{CEPR Discussion paper DP17346}. &    \\
   & &
   \\  

   & \textbf{How Did the European Marriage Pattern Persist? Social versus Familial Inheritance: England and Quebec, 1650--1850 }\\ 
   &   with Gregory Clark and Neil Cummins. Submitted. \href{https://hub.cepr.org/published-discussion-paper/170950}{CEPR Discussion paper DP17475}. & \\
   \\
   & \textbf{Seeds of Knowledge: Premodern Scholarship, Academic Fields, and European Growth }\\ 
   &   with David de la Croix. Submitted. \href{https://cepr.org/publications/dp18321}{CEPR Discussion paper DP18321}. & \\
   
   \\
   
   & \textbf{The Expansion of Public Education in Puerto Rico after 1900} &\\
   
   & with Mateo Uribe-Castro. Prepared for the book ``Roots of Underdevelopment: A New Economic (and Political) History of Latin America and the Caribbean,'' edited by Felipe Valencia-Caicedo. & \\
   \\
   
   
   
   \textbf{\large{Works in \(\phantom{1}\) Progress}}           & \textbf{Inheritance Customs, the European Marriage Pattern, and Female Empowerment}\\ 
   &  with Paula Gobbi, Marc Go\~{n}i, and Joanne Haddad. Funded by ERC Starting Grant 947654, IDED, granted to Paula Gobbi. &  \\
   \\
   &  \textbf{Resource Curses and Production Functions: Sugar, Coffee, and Schooling in Early 20th Century Puerto Rico} \\ 
   &  with  Mateo Uribe-Castro. \\
   \\
   &  \textbf{Before the Fall: Child Quantity and Quality in
   Pre-Demographic Transition Quebec} \\ 
   &   \\
   &  \textbf{Treating the Filles Like a Roi? --- Sex Ratios and Infant Mortality, Quebec 1620--1849} \\ 
   &   \\
   \\
   
   
   \textbf{\large{Teaching}}  & Business History & \hfill 2023 \\
   & Economic Development & \hfill 2021\\
   &  World Economic History Since the Industrial Revolution &\hfill 2019\\
   & Undergraduate Economic History Research Seminar & \hfill  2021 \\
   & Teaching Assistant 2016--2020\\
   
   \\
   
   \textbf{\large{Fellowships,}}   &  GSA Travel Award, UC Davis & \hfill  2020\\
   \textbf{\large{Honors and }}   &  \multicolumn{2}{l}{ Travel Grant, UC Davis Economics Department \hfill 2019}\\  
   \textbf{\large{Awards}}  &  \multicolumn{2}{l}{ Exploratory Travel and Data Grant, Economic History Association \hfill 2018}\\
   &  \multicolumn{2}{l}{ ISS Summer Research Support Award, UC Davis \hfill 2017}\\
   &  \multicolumn{2}{l}{ Grad Scholars Fellowship, UC Davis \hfill  2016}\\
   &  \multicolumn{2}{l}{ Phi Beta Kappa, Tufts Chapter, Delta of Massachusetts \hfill 2012}\\
   &   \multicolumn{2}{l}{ Daniel Ounjian Prize in Economics, Tufts Economics Department \hfill 2011}\\
   \\
   
   
   
   
   \textbf{\large{Presentations}} 
   & \multicolumn{2}{l}{ Economic History Association Annual Meeting   \hfill 2021, 2023}\\
   & World Cliometrics Conference &  \hfill 2023  \\
   & \multicolumn{2}{l}{ All UC Economic History Group Conference  \hfill 2023}\\
   &  Economic History Society Meeting & \hfill 2023\\
   & 12th Annual Workshop on ``Growth, History and Development'', SDU &  \hfill 2023\\
   & ``Religion, culture and economic growth in historical perspective'' &  \hfill 2023 \\ 
   & \hspace{4ex} Workshop, IRES UCLouvain, Poster Session \\
   & Danish  \& Scandinavian Societies for Economic and Social History Meeting &  \hfill 2022  \\
   & World Economic History Congress & \hfill 2022 \\
   & \multicolumn{2}{l}{  European Historical Economics Society Conference   \hfill 2019, 2022} \\
   & \multicolumn{2}{l}{ Annual Cliometric Conference    \hfill 2019, 2021, 2022} \\
   & IRES Seminar, UC Louvain & \hfill 2022 \\
   &  ``Sex Ratios and Missing Girls in History'' Conference & \hfill 2022\\
   & European Historical Demography Society Conference & \hfill 2022 \\
   & UNamur Internal Workshop & \hfill 2022 \\
   &   6th HEDG Mini Workshop for Young Scholars   & \hfill 2021\\
   & \multicolumn{2}{l}{ All UC Economic History Graduate Student Workshop  \hfill 2019, 2020}\\
   &  Economic History Association Annual Meeting Poster Session & \hfill  2020\\
   &  Economic History Society New Researcher Online Sessions & \hfill 2020\\
   &  YSI Economic History Graduate Seminar & \hfill 2020\\
   &  LSE Graduate Economic History Seminar & \hfill  2020\\
   &  Mountain West Economic History Conference  & \hfill  2019\\
   &  CAGE, EHES, and IAS Summer School  & \hfill  2017\\
   \\
   \textbf{\large{Refereeing}}   &   Journal of Economic History&\\
   &   European Review of Economic History &\\
\end{longtable}

% \noindent \begin{longtable}{@{} p{0.15\linewidth} p{0.4\linewidth} p{0.4\linewidth}}
%    \textbf{\large{References}}    &     Gregory Clark  & Paula Gobbi \\
   
%    & Professor &  Associate Professor \\
%    & Department of Economics & ECARES \\
%    & University of California, Davis & Universit\'{e} Libre de Bruxelles  \\
%    & \href{mailto:gclark@ucdavis.edu}{gclark@ucdavis.edu}  & \href{mailto:paula.eugenia.gobbi@ulb.be}{paula.eugenia.gobbi@ulb.be}  \\
%    \\
%    &  Katherine Eriksson  & Santiago P\'{e}rez  \\
%    & Associate Professor  &Assistant Professor  \\
%    & Department of Economics &   Department of Economics \\
%    & University of California, Davis & University of California, Davis  \\
%    & \href{mailto:kaeriksson@ucdavis.edu}{kaeriksson@ucdavis.edu}& \href{mailto:seperez@ucdavis.edu}{seperez@ucdavis.edu}   \\
% \end{longtable}



%-----------------------------------------------------------------------------%
\end{document}

