%=============================================================================%
%Change the font size of your document - 10pt, 12.1pt, etc.
\documentclass[a4paper,11pt,oneside]{article}
\usepackage[utf8]{inputenc}
\usepackage{setspace}
\usepackage{hyperref}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{hyperref}

\graphicspath{ {images/}} %upload your signature to this file
%Change the margins to fit your CV/resume content
\usepackage[left=1in, right=1in, bottom=1.25in, top=1.25in]{geometry}


%Changes the page numbers - {arabic}=arabic numerals, {gobble}=no page numbers, {roman}=Roman numerals
\pagenumbering{gobble}
%=============================================================================%
\begin{document}

%-----------------------------------------------------------------------------%

\noindent  \LARGE{\textbf{Matthew J. D. Curtis}}  \\

%\hline 
\normalsize



%-----------------------------------------------------------------------------%

\noindent \begin{longtable}{@{} p{0.175\linewidth} p{0.775\linewidth} p{0.05\linewidth}}


  
 \textbf{\large{Contact}}    &  \multicolumn{2}{l}{Email: \href{mailto:matthew.curtis@ulb.be}{matthew.curtis@ulb.be} }\\
   \textbf{\large{Information}}  &  \multicolumn{2}{l}{Website: \href{https://www.mjdcurtis.com/}{www.mjdcurtis.com} }\\
   &  \multicolumn{2}{l}{Phone: +32~491939150}\\
      &  \multicolumn{2}{l}{Address: 16 Avenue Dolez, \#1, Uccle 1180, Belgium}\\
      \\ 

      \textbf{\large{Employment}}    & \multicolumn{2}{l}{\textbf{ECARES, Universit\'{e} libre de Bruxelles }} \\
      &  \multicolumn{2}{l}{ Postdoctoral researcher \hfill  2021-}\\
    \\
 \textbf{\large{Education}}    & \multicolumn{2}{l}{\textbf{University of California, Davis}} \\
     &  \multicolumn{2}{l}{ Ph.D., Economics \hfill  2021}\\
   &   \multicolumn{2}{l}{ Committee: Gregory Clark (Chair), Katherine Eriksson, Santiago P\'{e}rez}\\

   \\
     & \multicolumn{2}{l}{ \textbf{Tufts University},}\\
     & \multicolumn{2}{l}{B.A. Quantitative Economics and Mathematics \hfill  2012}\\
     & \multicolumn{2}{l}{Magna Cum Laude  with High Thesis Honors   }\\
     &  \multicolumn{2}{l}{ }\\
     \textbf{\large{Fields}}    &  \multicolumn{2}{l}{ Economic History,  Labor Economics, Economic Development}\\
     \\

     \textbf{\large{Publications}}   & \textbf{Twins Support Absence of Parity-Dependent Fertility Control in Pretransition Populations }\\
    %& \parbox{5.0in}{ September 2019 – }}\\
     &  with Gregory Clark and Neil Cummins. \href{https://read.dukeupress.edu/demography/article/57/4/1571/168109/Twins-Support-the-Absence-of-Parity-Dependent}{\emph{Demography}}. & \hfill 2020\\
     \\  


     \textbf{\large{Working \(\phantom{1}\)  Papers}}  & \textbf{The Her in Inheritance: How Marriage Matching Has Always Mattered, Quebec 1800--1970}\\ 
     &  Job market paper. Submitted. &  \\
        & &
       \\

    & \textbf{The Mismeasure of Man: Why Intergenerational Occupational Mobility  is Much Lower than Conventionally Measured, England, 1800--2021}\\ 
    &  with Gregory Clark and Neil Cummins. Submitted. \href{https://hub.cepr.org/published-discussion-paper/139739}{CEPR Discussion paper DP17346}. &    \\
       & &
      \\  
      & \textbf{Three New Occupational Status Indices for England and Wales, 1800--1939}\\ 
      &  with Gregory Clark and Neil Cummins. Submitted. &   \\
     \\

 & \textbf{How Did the European Marriage Pattern Persist? Social versus Familial Inheritance: England and Quebec, 1650--1850 }\\ 
     &   with Gregory Clark and Neil Cummins. Submitted. \href{https://hub.cepr.org/published-discussion-paper/170950}{CEPR Discussion paper DP17475}. & \\
      \\

      \\
     &  \textbf{Was There A Crisis? A Human Development Index for Lower Canada, 1760 to 1848 } \\ 
      &   with Vincent Geloso. Submitted. \href{https://papers.ssrn.com/sol3/papers.cfm?abstract_id=4200516}{SSRN working paper}. &  \\
      \\ 
 
      & \textbf{The Expansion of Public Education in Puerto Rico after 1900} &\\

      & with Mateo Uribe-Castro. Prepared for the book ``Roots of Underdevelopment: A New Economic (and Political) History of Latin America and the Caribbean,'' edited by Felipe Valencia-Caicedo. & \\
  \\


     
     \textbf{\large{Works in \(\phantom{1}\) Progress}}           & \textbf{Inheritance Customs, the European Marriage Pattern, and Female Empowerment}\\ 
     &  with Paula Gobbi, Marc Go\~{n}i, and Joanne Haddad. Funded by ERC Starting Grant 947654, IDED, granted to Paula Gobbi. &  \\
       \\
       &  \textbf{Resource Curses and Production Functions: Sugar, Coffee, and Schooling in Early 20th Century Puerto Rico} \\ 
      &  with  Mateo Uribe-Castro. \\
      \\
      &  \textbf{Before the Fall: Child Quantity and Quality in
      Pre-Demographic Transition Quebec} \\ 
      &   \\
      &  \textbf{Treating the Filles Like a Roi? --- Sex Ratios and Infant Mortality, Quebec 1620--1849} \\ 
      &   \\
      \\


     \textbf{\large{Teaching}} &  \textbf{Associate Instructor} & \\
      & Economic Development & \hfill 2021\\
     &  World Economic History Since the Industrial Revolution &\hfill 2019\\
     \\ 
     &   \textbf{Co-Instructor} \\
     & Undergraduate Economic History Research Seminar & \hfill  2021 \\
     \\ 
     & \textbf{Teaching Assistant} &\\

     &  \multicolumn{2}{l}{ US Economic History after 1865 \hfill 2018, 2019, 2020 }\\
     &  World Economic History Before the Industrial Revolution & \hfill 2019\\
     &  History of the United States Since 1865 & \hfill 2019\\
     &  World Economic History Before the Industrial Revolution & \hfill 2019\\
     &  World Economic History Since the Industrial Revolution & \hfill 2017\\
     &  Poverty, Inequality, and Public Policy & \hfill 2017\\
     &  US Economic History Before 1865 & \hfill 2016 \\

     \\


  \textbf{\large{Work }}    &  \multicolumn{2}{l}{ \textbf{Graduate Student Researcher}}\\
  \textbf{\large{Experience}}     &  \multicolumn{2}{l}{ Research assistant for Gregory Clark \hfill 2017 -- 2021 }\\

     &  \multicolumn{2}{l}{ Research assistant for Katherine Eriksson \hfill 2018}\\
    &  \multicolumn{2}{l}{ \textbf{Senior Research Assistant } }\\
    &  \multicolumn{2}{l}{ Federal Reserve Bank of Boston \hfill   2012 -- 2015}\\
    % &  \multicolumn{2}{l}{ Research assistant for Christopher Foote}\\
     \\
     \\

 \textbf{\large{Fellowships,}}   &  GSA Travel Award, UC Davis & \hfill  2020\\
  \textbf{\large{Honors and }}   &  \multicolumn{2}{l}{ Travel Grant, UC Davis Economics Department \hfill 2019}\\  
  \textbf{\large{Awards}}  &  \multicolumn{2}{l}{ Exploratory Travel and Data Grant, Economic History Association \hfill 2018}\\
  &  \multicolumn{2}{l}{ ISS Summer Research Support Award, UC Davis \hfill 2017}\\
  &  \multicolumn{2}{l}{ Grad Scholars Fellowship, UC Davis \hfill  2016}\\
  &  \multicolumn{2}{l}{ Phi Beta Kappa, Tufts Chapter, Delta of Massachusetts \hfill 2012}\\
  &   \multicolumn{2}{l}{ Daniel Ounjian Prize in Economics, Tufts Economics Department \hfill 2011}\\
  \\


      

 \textbf{\large{Presentations}}    & Danish  \& Scandinavian Societies for Economic and Social History Meeting &  \hfill 2022  \\
 & World Economic History Congress & \hfill 2022 \\
 & \multicolumn{2}{l}{  European Historical Economics Society Conference   \hfill 2019, 2022} \\
 & \multicolumn{2}{l}{ Annual Cliometric Conference    \hfill 2019, 2021, 2022} \\
 & IRES Seminar, UC Louvain & \hfill 2022 \\
 &  ``Sex Ratios and Missing Girls in History'' Conference & \hfill 2022\\
 & European Historical Demography Society Conference & \hfill 2022 \\
 & UNamur Internal Workshop & \hfill 2022 \\
 &   6th HEDG Mini Workshop for Young Scholars   & \hfill 2021\\
 &   Economic History Association Annual Meeting   & \hfill 2021\\
 & \multicolumn{2}{l}{ All UC Economic History Graduate Student Workshop  \hfill 2019, 2020}\\

   &  Economic History Association Annual Meeting Poster Session & \hfill  2020\\
   &  Economic History Society New Researcher Online Sessions & \hfill 2020\\
  &  YSI Economic History Graduate Seminar & \hfill 2020\\
   &  LSE Graduate Economic History Seminar & \hfill  2020\\
     &  Mountain West Economic History Conference  & \hfill  2019\\
     &  CAGE, EHES, and IAS Summer School  & \hfill  2017\\
     \\
     \textbf{\large{Refereeing}}   &   European Review of Economic History &\\

   
    \end{longtable}

    \noindent \begin{longtable}{@{} p{0.15\linewidth} p{0.4\linewidth} p{0.4\linewidth}}
     \textbf{\large{References}}    &     Gregory Clark  & Paula Gobbi \\

     & Professor &  Associate Professor \\
     & Department of Economics & ECARES \\
     & University of California, Davis & Universit\'{e} Libre de Bruxelles  \\
     & \href{mailto:gclark@ucdavis.edu}{gclark@ucdavis.edu}  & \href{mailto:paula.eugenia.gobbi@ulb.be}{paula.eugenia.gobbi@ulb.be}  \\
     \\
     &  Katherine Eriksson  & Santiago P\'{e}rez  \\
     & Associate Professor  &Assistant Professor  \\
     & Department of Economics &   Department of Economics \\
     & University of California, Davis & University of California, Davis  \\
     & \href{mailto:kaeriksson@ucdavis.edu}{kaeriksson@ucdavis.edu}& \href{mailto:seperez@ucdavis.edu}{seperez@ucdavis.edu}   \\
      \end{longtable}



%-----------------------------------------------------------------------------%
\end{document}

